Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-25 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
reformatted table

\begin{table*}[t]
\begin{tabular}{c | c c c c c c c c c c}
\hline
\hline
Theory      & $\omega^{(0)}_{220}$ & $\tau^{(0)}_{220}$ & $\omega^{(1)}_{220}$ & $\tau^{(1)}_{220}$ & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & Ref.  \\
\hline
GR          & 0.3737               & 11.2407            &  0.1258              & 0.2522             & --  & --                          & --                        & --                          & --                        & \cite{Maselli:2019mjd} \\
\hline
EdGB        & --                   & --                 &  --                  & --                 & 4   & 0.0107                      & 0.0044                    & $-$0.2480                   & $-$1.101                  & \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
dCS         & --                   & --                 &  --                  & --                 & 4   & 3.1964                      & 6.3619                    & 41.199                      & 794.66                    & \cite{Wagle:2021tam}  \\
cubic EFT   & --                   & --                 &  --                  & --                 & 4   & $-$0.5813                   & 2.6469                    & $-$3.8620                   & 265.12                    & \cite{Cano:2021myl} \\
quartic EFT & --                   & --                 &  --                  & --                 & 6   & $-$0.2114                   & $-$0.6070                 & $-$1.5263                   & 171.35                    & \cite{Cano:2021myl}  \\
\hline
\hline
\end{tabular}
\caption{Summary of theory-specific QNM calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(n)}_{220}$ and decay time $\delta \tau^{(n)}_{220}$, and the
references from which we used the results from.
%
We also included for comparison the GR coefficients, up to $j=1$, obtained in Ref.~\cite{Maselli:2019mjd}.
%
The remaining GR coefficients for $1< j \leqslant 4$, for which their non-GR counterpart cannot be determined as of yet for
the theories under consideration, can be found in Table~I of Ref.~\cite{Maselli:2019mjd}.
}
\label{tab:ref_theories_qnms}
\end{table*}

>>>>

\begin{table*}[t]
% \begin{tabular}{c | c c c c c c c c c c}
% \hline
% \hline
% Theory      & $\omega^{(0)}_{220}$ & $\tau^{(0)}_{220}$ & $\omega^{(1)}_{220}$ & $\tau^{(1)}_{220}$ & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & Ref.  \\
% \hline
% GR          & 0.3737               & 11.2407            &  0.1258              & 0.2522             & --  & --                          & --                        & --                          & --                        & \cite{Maselli:2019mjd} \\
% \hline
% EdGB        & --                   & --                 &  --                  & --                 & 4   & 0.0107                      & 0.0044                    & $-$0.2480                   & $-$1.101                  & \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
% dCS         & --                   & --                 &  --                  & --                 & 4   & 3.1964                      & 6.3619                    & 41.199                      & 794.66                    & \cite{Wagle:2021tam}  \\
% cubic EFT   & --                   & --                 &  --                  & --                 & 4   & $-$0.5813                   & 2.6469                    & $-$3.8620                   & 265.12                    & \cite{Cano:2021myl} \\
% quartic EFT & --                   & --                 &  --                  & --                 & 6   & $-$0.2114                   & $-$0.6070                 & $-$1.5263                   & 171.35                    & \cite{Cano:2021myl}  \\
% \hline
% \hline
% \end{tabular}
%
\begin{tabular}{c | c }
\hline
\hline
Theory                  & GR~\cite{Maselli:2019mjd} \\
\hline
$\omega^{(0)}_{220}$    & 0.3737                    \\
$\tau^{(0)}_{220}$      & 11.2407                   \\
$\omega^{(1)}_{220}$    & 0.1258                    \\
$\tau^{(1)}_{220}$      & 0.2522                    \\
\hline
\hline
\end{tabular}
\quad
\begin{tabular}{c | c  c  c  c}
\hline
\hline
Theory                        & EdGB ($p=4$)~\cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} & dCS ($p=4$)~\cite{Wagle:2021tam} & cubic EFT ($p=4$)~\cite{Cano:2021myl} & quartic EFT ($p=6$)~\cite{Cano:2021myl} \\
\hline
$\delta\omega^{(0)}_{220}$    & 0.0107                                               & 3.1964                   & $-$0.5813                     & $-$0.2114                       \\
$\delta\tau^{(0)}_{220}$      & 0.0044                                               & 6.3619                   & $-$0.2114                     & $-$0.6070                       \\
$\delta\omega^{(1)}_{220}$    & $-$0.2480                                            & 41.199                   & $-$3.8620                     & $-$1.5263                       \\
$\delta\tau^{(1)}_{220}$      & $-$1.1010                                            & 794.66                   & 265.12                        & 171.35                          \\
\hline
\hline
\end{tabular}
\caption{Summary of theory-specific QNM calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(n)}_{220}$ and decay time $\delta \tau^{(n)}_{220}$, and the
references from which we used the results from.
%
We also included for comparison the GR coefficients, up to $j=1$, obtained in Ref.~\cite{Maselli:2019mjd}.
%
The remaining GR coefficients for $1< j \leqslant 4$, for which their non-GR counterpart cannot be determined as of yet for
the theories under consideration, can be found in Table~I of Ref.~\cite{Maselli:2019mjd}.
}
\label{tab:ref_theories_qnms}
\end{table*}
